A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-08-08 sections/05-responses.tex
Minor edits to responses

The course of Concurrent, Parallel and Distributed Computing is offered to
students of both the graduate and undergraduate programs in Computer Science at
the University of São Paulo. To gauge the proficiency and knowledge of our
students we elaborated a five-point scale from \textit{Do not Know} $(1)$ to
\textit{Expert or Proficient} $(5)$.  The students were asked to express their
proficiency level on this scale, and their responses are shown in Figure
\ref{fig:background}.

@@

The students were asked to evaluate their proficiency in \textit{OpenMP} and
\textit{Pthreads}, \textit{before} completing the assignment, with two sets of
questions. The first set used the same five-point scale as the other background
questions and is also shown in Figure \ref{fig:background}. The students
reported significantly larger proficiency in \textit{Pthreads} than
\textit{OpenMP}, and the majority of the students reported they did not know
\textit{OpenMP} before the course.

@@

The students were asked to answer 3 sets of questions regarding their
experience with \textit{OpenMP} and \textit{Pthreads}, \textit{after}
completing the assignment.
The first set of questions used a Likert-type Scale to measure the relationship
of the students with the two APIs in the context of the assignment. The Likert
Scale~\cite{likert1932technique} enables respondents to express their agreement
or disagreement with specific statements. Respondents choose between five
options: \textit{Strongly Agree} (SA), \textit{Agree} (A), \textit{Neutral}
(N), \textit{Disagree} (D) and \textit{Strongly Disagree}.

>>>>

The course of Concurrent, Parallel and Distributed Computing is offered to
students of both the graduate and undergraduate programs in Computer Science at
the University of São Paulo. To gauge the proficiency and knowledge of our
students we elaborated a five-point scale from \textit{Do not Know} $(1)$ to
\textit{Expert or Proficient} $(5)$.  We asked the students to express their
proficiency level on this scale, and their responses are shown in Figure
\ref{fig:background}.

@@

We asked the students to evaluate their proficiency in \textit{OpenMP} and
\textit{Pthreads}, \textit{before} completing the assignment, with two sets of
questions. The first set used the same five-point scale as the other background
questions and is also shown in Figure \ref{fig:background}. The students
reported significantly larger proficiency in \textit{Pthreads} than
\textit{OpenMP}, and the majority of the students reported they did not know
\textit{OpenMP} before the course.

@@

We asked the students to answer 3 sets of questions regarding their
experience with \textit{OpenMP} and \textit{Pthreads}, \textit{after}
completing the assignment.
The first set of questions used a Likert-type Scale to measure the relationship
of the students with the two APIs in the context of the assignment. The Likert
Scale~\cite{likert1932technique} enables respondents to express their agreement
or disagreement with specific statements. Respondents choose between five
options: \textit{Strongly Agree} (SA), \textit{Agree} (A), \textit{Neutral}
(N), \textit{Disagree} (D) and \textit{Strongly Disagree}.
